Multi-resolution Neural Field Estimation

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
suggestions for cutting

The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008} \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165]. (This is copy and paste from my thesis ... parham I'll get you the references later)}. \parham{Mike,Ken: can add to this list?}

@@

Future work should be directed towards extending the framework to account heterogeneity and perhaps time delays at lower spatial resolutions. Another useful extensions would be the inclusion of a second-order synaptic response kernel to enrich the dynamics from the model. Most importantly, future work should be directed towards applying and validating the framework on real data.

>>>>

\cut{The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008} \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165]. (This is copy and paste from my thesis ... parham I'll get you the references later)}. \parham{Mike,Ken: can add to this list?}}

@@

Future work should be directed towards extending the framework to account heterogeneity and perhaps time delays at lower spatial resolutions.\cut{ Another useful extensions would be the inclusion of a second-order synaptic response kernel to enrich the dynamics from the model.} Most importantly, future work should be directed towards applying and validating the framework on real data.
